
# Basic Algorithm

## Requirements
* Keep functions vectorised

### Discovery

* Uniform Distribution
* Capital / cost of teams = max teams
* Min teams = 0
* Actual teams = Calc teams + 1
* prob of finding = rnbinom(10000, 1, 0.15) - 10,000 obs, how many trials did it take for atleast one success, 0.15 prob of sucess.
* actual teams >= calc teams claim discovered
* Discovered moves right


```{r}

discoverfunc <- function(capital, cost, prob) {
  numb <- length(capital)
  maxteam <- capital / cost
  minteam <- 0
  calcteam <- runif(numb, minteam, maxteam)
  searches <- 1 + calcteam
  searchesneeded <- rnbinom(numb, 1, prob)
  discovered = searchesneeded - searches
  # remove values of 1
  discovered <- discovered + discovered
  discovered[discovered <= 0] <- 1
  discovered[discovered != 1] <- 0
  return(discovered)
}

```

### Legal Fees

* Uniform distribution, 50% prob of of responding
* if respond 40% chance of success

```{r}
legalfunc <- (chooserespondprob){
  chosetorespond <- runif(numb)
  discovered[discovered >= 1-chooserespondprob] <- 1
  discovered[discovered != 1] <- 0
}
  
  
```

## Algorithm

```{r}

Starting_capital <- 2e6
n <- 1e4


#montemonte <- function (n, starting.capital, gold.startprice, gold.min, gold.ml, gold.max) {

gprice.y1 <- rep(2500, n)
gprice.y2 <- pricesim$change2 <- rpert(n = n, x.min = vmin, x.max = vmax, x.mode = vml, lambda = lambda)
pricesim$year2 <- pricesim$year1 + pricesim$change2

```

